\vfill A Testing Framework for Web Applications

### 2014-03-12 Paper/paper.tex
Lots of stubbing. Commit mostly so I can switch computers.

\subsubsection{Intern}

% Browser Testing!
\subsubsection{Selenium}

\subsubsection{PhantomJS}

\subsubsection{ZombieJS}

@@

\subsubsection{Nightwatchjs}

>>>>

\subsubsection{Intern\cite{InternIO}}
Intern is a hybrid unit testing and browser testing framework that aims to be an all-in-one testing framework.
- BDD, TDD, Object Testing methods
- Integration with Selenium
- Distinction between non-functional and functional tests
- Code Coverage!

% Browser Testing!
\subsubsection{Selenium\cite{Selenium}}
- HAD TO EDIT APP.JS TO USE NEW JAR
- HAD TO ADD NEW JAR!

\subsubsection{Nightwatchjs\cite{NightwatchJS}}
- Selenium WebDriver driver
- Browser-only

\subsubsection{PhantomJS\cite{PhantomJS}}
Too much.
- Really great though, could be useful if needed.
- Slow
- FULL DOM/Browser emulation

\subsubsection{ZombieJS\cite{ZombieJS}}
- Lightweight
- Headless
- NOT Full DOM emulation

@@
